\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[a4paper, total={6in, 8in}]{geometry}

\title{Notes on Chapter 6 - Testing and Debugging}
\author{Swarup Tripathy \thanks{John V Guttag}}
\date{February 2022}


\begin{document}
    \maketitle
    A curated list of important points for my reference.\\
    \begin{enumerate}
        \item \textbf{Black Box Testing} \href{https://www.youtube.com/watch?v=H7k3R1_A_yI}{Intrigano}
        \begin{itemize}
            \item Black box is referred to a box covered in Black such that we can't see inside of it.
            \item Here the test suite is designed without actually looking at the code.
            \begin{enumerate}
                \item Can be done by someone other than implementer
                \item Will avoid inherent biases of implementer, exposing potential bugs more easily
                \item Testing designed without knowledge of implementation, thus can be reused even if implementation changed.
            \end{enumerate}
        \end{itemize}
        \item \textbf{Glass Box Testing} \href{https://www.youtube.com/watch?v=cpJ5AjRl8gI}{Intrigano}
        \begin{itemize}
            \item Complementary to black box testing.
            \item Since the name itself implies we can actually see inside the box or the code.
            \begin{enumerate}
                \item Use code directly to guide design of test cases
                \item Glass box test suite is \textbf{path-complete} if every potential path through the code is tested atleast once.
                \begin{enumerate}
                    \item Not always possible if loop can be exercised arbitrary times, or recursion can be arbitrarily deep.
                \end{enumerate}
                \item even a path complete test suite can have a bug, depending on choice of samples. 
            \end{enumerate}
            \item Rules of thumb for glass box testing
            \begin{enumerate}
                \item exercise both branches of all if statements
                \item ensure each except clause is executed
                \item for each for loop, have tests where
                \begin{enumerate}
                    \item loop is not entered
                    \item body of loop executed exactly once
                    \item body of loop executed more than once
                \end{enumerate}
                \item For each While loop
                \begin{enumerate}
                    \item same cases as for loops
                    \item cases that catch all ways to exit loop
                \end{enumerate}
                \item For recursive functions, test with no recursive calls, once recursive call, and more than one recursive call.
            \end{enumerate}
        \end{itemize}
    \end{enumerate}
\end{document}